|

### 2021-12-08 index.Rmd
Remove covering page and apply comma to wordcount

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy
degreedate: December 2021
word-count: |
  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last()`
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
covidStatment: |
  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

@@

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: false   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: false # add as DRAFT mark in the footer?
page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-toc-depth: 1
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?

>>>>

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy
degreedate: December 2021
word-count: |
  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last() %>% comma()`
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
covidStatment: |
  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

@@

#####################
## PDF formatting  ##
#####################
abstractseparate: false  # include front page w/ abstract for examination schools?
bib-humanities: false   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: false # add as DRAFT mark in the footer?
page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-toc-depth: 1
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?
